PK object batch mode trial

### 2023-06-15 data-raw/batchMode_trial_gpm.Rmd
Updated the coef method to include keep_sigma, model, and method arguments. coef() now includes linked sigma_value and error_group columns

```{r coef_function_remake}
# A list of each fit model with the estimated parameters for that model
pk_results <- coef(my_pk) # NAs are printed

@@

my_coefs_update <- coef(my_pk, model = "model_flat", drop_sigma = TRUE)
my_pred_update <- predict(my_pk,
                          use_scale_conc = TRUE)

>>>>

```{r coef_function_remake}
# A list of each fit model with the estimated parameters for that model
pk_results <- coef(my_pk)

@@

my_coefs_update <- coef(my_pk, drop_sigma = TRUE)
my_pred_update <- predict(my_pk,
                          use_scale_conc = TRUE)
